Nested sampling with two objective functions

### 2015-11-28 Paper/ms.tex
More writing

Consider running standard NS using the objective function $L_1(\xx)$. After some
time, we'd know the function $X(\ell_1) = \int \pi(\xx) \, d\xx$

>>>>

Consider running standard NS with $N$ particles
using the objective function $L_1(\xx)$.
After $M$ iterations, we'd be able to approximate
the function $X(\ell_1) = \int \pi(\xx) \, d\xx$
from $X\approx e^{-M/N}$ to $X=1$. Defining $Y=-\ln(X)$, we could also
construct an approximation to the function
$L(Y)$, a non-decreasing function of $Y$, from $Y=0$ to $Y\approx M/N$.
